Job Demands-Resources model components through the lens of O*NET classifications

### 2022-11-11 Submission.Rmd
udpated submission.rmd file with our new notes and predictions.

@@

Looked through

@@

While Study 1 explored the above questions across jobs, Study 2 considers a potentially important moderator: job classification. There is a distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework depending on *job classification*. In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., [@bakker2013weekly]; [@cavanaugh2000empirical]; [@gerich2017relevance]; [@podsakoff2007differential]; [@webster2011extending]). Thus, Study 2 focuses on a fourth question of interest.

>*Research Question 4*: Does the **type of work** reported explain variability in the categorization of work characteristics into challenges, hindrances, and resources?

@@

>>>>

>Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.

>Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.

Add a description here of the exploratory stuff.

@@

@@

@@

```{r scale-level-graphs eval = FALSE}
#this is a placeholder for the scale level faceted graph found in plotscript_practice script file. 
```

### 2022-11-11 Submission.tex
udpated submission.rmd file with our new notes and predictions.

Of the 785 Prolific panel individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (\textbf{R-careless?}). Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current SIOP sample. 13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.

@@

>>>>

Of the 785 Prolific panel individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021). Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current SIOP sample. 13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.

@@

\leavevmode\hypertarget{ref-R-careless}{}%
Yentes, R. D., \& Wilhelm, F. (2021). \emph{Careless: Procedures for computing indices of careless responding}.
